Supplementary information: In-silico molecular enrichment and clearance of the human intracranial space

### 2025-06-20 paper/supplementary.tex
Fix typos.

Investigating the link between cardiac pulsatility and the resulting diffusion enhancement factor, we compute for $R$ different levels of cardiac pulsatility. We reduce the inflow boundary conditions of $6\,$ml/s (across the SAS outer surface) and $0.31\,$ml/s (across the lateral ventricle surface) by $25\,\%$, $50\,\%$, $75\,\%$ and $100\,\%$ to model lower cardiac pulsatility, reaveling that $R$ scales quadratically with the reduction of inflow (\cref{fig:R_comparison}). This behaviour directly reflects the nature of our model - the Stokes flow is linear in its boundary conditions, and the diffusion enhancement factor quadratic in the predicted pressure gradient - and simultaneously underscores the substantial role of pulsatility in shaping intracranial transport.

\begin{figure}
    \centering
    \includegraphics[width=1.0\linewidth]{figures/cardiac_R_comparison.png}
    \caption{Comparison of cardicac-driven diffusion enhancement factors for different levels of cardiac pulsatility. From left to right: The diffusion enhancement factor $R_c$ for $25\,\%$, $50\,\%$, $75\,\%$ and $100\,\%$ of the inflow boundary conditions of $6\,$ml/s and $0.31\,$ml/s across the SAS outer surface and the lateral ventricle surface, respectively.}
    \label{fig:R_comparison}
\end{figure}

>>>>

Investigating the link between cardiac pulsatility and the resulting diffusion enhancement factor, we compute for $R$ different levels of cardiac pulsatility. We reduce the inflow boundary conditions of $6\,$ml/s (across the SAS outer surface) and $0.31\,$ml/s (across the lateral ventricle surface) by $25\,\%$, $50\,\%$, $75\,\%$ and $100\,\%$ to model lower cardiac pulsatility, revealing that $R$ scales quadratically with the reduction of inflow (\cref{fig:R_comparison}). This behaviour directly reflects the nature of our model - the Stokes flow is linear in its boundary conditions, and the diffusion enhancement factor quadratic in the predicted pressure gradient - and simultaneously underscores the substantial role of pulsatility in shaping intracranial transport.

\begin{figure}
    \centering
    \includegraphics[width=1.0\linewidth]{figures/cardiac_R_comparison.png}
    \caption{Comparison of cardiac-driven diffusion enhancement factors for different levels of cardiac pulsatility. From left to right: The diffusion enhancement factor $R_c$ for $25\,\%$, $50\,\%$, $75\,\%$ and $100\,\%$ of the inflow boundary conditions of $6\,$ml/s and $0.31\,$ml/s across the SAS outer surface and the lateral ventricle surface, respectively.}
    \label{fig:R_comparison}
\end{figure}
